\textbf{Differences in COVID-19 vaccination in the province of Ontario across Health Regions and socio-economic strata}

### 2023-06-09 manuscript_v5/02-methods.qmd
updated manuscript following BN comments

By design, the survey allowed respondents to exit at any time and deployed the questions randomly, which resulted in $\approx$ 84\% of the observations having multiple missing answers or being incomplete. Therefore, we selected 6,343 observations that were labelled as "complete" in the dataset and that had answers for all covariates considered in our analysis. Later, we matched the city of each observation with its corresponding LHIN and Health Region, and removed observations from areas with low representation (254 observations corresponding to the North West and North East Health Regions). Finally, we removed outliers from the data (19 observations of individuals under 25 years of age with household size of 1 and income above 110,000 CAD in the original dataset, that were demeed to lack accuracy). After all the preliminary analyses, the total number of observations used for analysis was 6,236 and included the East, Central, Toronto, and West Health Regions covering between October 1st,2021 and January 17, 2022. The original dataset, clean dataset, and details on the data cleaning process are described in detail in the [GitHub repository](https://github.com/aimundo/Fields_COVID-19/) for this paper.

>>>>

By design, the survey allowed respondents to exit at any time and deployed the questions randomly. This resulted in $\approx$ 84\% of the observations having multiple missing answers or being incomplete due to participants leaving the survey at different stages. Therefore, we selected 6,343 observations that were labelled as "complete" in the dataset and that had answers for all covariates considered in our analysis. Later, we matched the city of each observation with its corresponding LHIN and Health Region, and removed observations from areas with low representation (254 observations corresponding to the North West and North East Health Regions). After all the preliminary analyses, the total number of observations used for analysis was 6,236 and included the East, Central, Toronto, and West Health Regions covering between October 1st,2021 and January 17, 2022. The original dataset, clean dataset, and details on the data cleaning process are described in detail in the [GitHub repository](https://github.com/aimundo/Fields_COVID-19/) for this paper.

### 2023-06-09 manuscript_v5/main.tex
updated manuscript following BN comments

\date{}
\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, enhanced, sharp corners, borderline west={3pt}{0pt}{shadecolor}, interior hidden, frame hidden, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

By design, the survey allowed respondents to exit at any time and
deployed the questions randomly, which resulted in \(\approx\) 84\% of
the observations having multiple missing answers or being incomplete.
Therefore, we selected 6,343 observations that were labelled as
``complete'' in the dataset and that had answers for all covariates
considered in our analysis. Later, we matched the city of each
observation with its corresponding LHIN and Health Region, and removed
observations from areas with low representation (254 observations
corresponding to the North West and North East Health Regions). Finally,
we removed outliers from the data (19 observations of individuals under
25 years of age with household size of 1 and income above 110,000 CAD in
the original dataset, that were demeed to lack accuracy). After all the
preliminary analyses, the total number of observations used for analysis
was 6,236 and included the East, Central, Toronto, and West Health
Regions covering between October 1st,2021 and January 17, 2022. The
original dataset, clean dataset, and details on the data cleaning
process are described in detail in the
\href{https://github.com/aimundo/Fields_COVID-19/}{GitHub repository}
for this paper.

@@

Moreover, the recent nature in the adaption of the Health Region poses a
challenge for researchers in the acquisition of data and information
that can be used to analyze the performance of the new system. From one
side, the Health Regions have not been incorporated as part of Census
data (LHINs were considered before in the Census), and this impact the
amount and level of detail of available information. Currently, the only
demographic information available for each Health Region is provided by
Ontario Health (the agency that administers the Health Regions) but this
information only provides general estimates that do not allow for
detailed analyses of performance indicators (such as hospitalizations,
readmissions, and trends in chronic disease incidence) between the
regions. Without open information, it is impossible to assess the level
of success of the Health Region model, which is critical considering
that such evaluations have not been part of the Annual Reports of the
Auditor General of Ontario, which in the past analyzed the performance
of the LHINs and pointed to ongoing needs and failures in the system.

>>>>

\date{}
\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, boxrule=0pt, interior hidden, frame hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, breakable]}{\end{tcolorbox}}\fi

@@

By design, the survey allowed respondents to exit at any time and
deployed the questions randomly. This resulted in \(\approx\) 84\% of
the observations having multiple missing answers or being incomplete due
to participants leaving the survey at different stages. Therefore, we
selected 6,343 observations that were labelled as ``complete'' in the
dataset and that had answers for all covariates considered in our
analysis. Later, we matched the city of each observation with its
corresponding LHIN and Health Region, and removed observations from
areas with low representation (254 observations corresponding to the
North West and North East Health Regions). After all the preliminary
analyses, the total number of observations used for analysis was 6,236
and included the East, Central, Toronto, and West Health Regions
covering between October 1st,2021 and January 17, 2022. The original
dataset, clean dataset, and details on the data cleaning process are
described in detail in the
\href{https://github.com/aimundo/Fields_COVID-19/}{GitHub repository}
for this paper.

@@

Moreover, the recent nature in the adaption of the Health Region poses a
challenge for researchers in the acquisition of data and information
that can be used to analyze the performance of the new model. From one
side, the Health Regions have not been incorporated as part of Census
data (LHINs were considered before in the Census), and this impact the
amount and level of detail of available information. On the other hand,
evaluations of the Health Region model are at the moment not considered
in the Annual Reports of the Auditor General of Ontario, which was
critical in the past to identify limitations in the LHIN model.
Currently, the only demographic information available for each Health
Region is provided by Ontario Health (the agency that administers the
Health Regions) but this information only provides general estimates
that do not allow for detailed analyses of performance indicators (such
as hospitalizations, readmissions, and trends in chronic disease
incidence) between the Regions. Therefore, there is a pressing need for
open data that can be used by researchers and decision-makers to examine
the performance of the Health Region model.
